Format for lefse and run on the classes CR and tox

### 2019-10-30 scripts/03_lefse_CR_tox.Rmd
use cpm instead of relab

```{r}
# input: relative abundance unstratified for pathway abundance
relab <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_relab_unstratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # remove the unmapped and the unintegrated record
  filter(!sampleid %in% c('UNMAPPED','UNINTEGRATED'))

@@

# write out the table
relab_or %>% 
  write_tsv('../data/pheno_aligned_relab_table/humann2_pathabundance_relab_unstratified.tsv')
```

@@

pheno_combi %>% 
  mutate(cat_cmd = str_glue('cat {pheno_file} ../data/pheno_aligned_relab_table/humann2_pathabundance_relab_unstratified.tsv > ../data/lefse_input/pathway_abundace_{combi}tsv')) %>% 
  select(cat_cmd) %>% 
  write_csv('cat_combi_CT.sh', col_names = F)
```

>>>>

```{r}
# input: relative abundance unstratified for pathway abundance
relab <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # remove the unmapped and the unintegrated record
  filter(!sampleid %in% c('UNMAPPED','UNINTEGRATED'))

@@

# write out the table
relab_or %>% 
  write_tsv('../data/pheno_aligned_relab_table/humann2_pathabundance_cpm_unstratified.tsv')
```

@@

pheno_combi %>% 
  mutate(cat_cmd = str_glue('cat {pheno_file} ../data/pheno_aligned_relab_table/humann2_pathabundance_cpm_unstratified.tsv > ../data/lefse_input/pathway_abundace_{combi}tsv')) %>% 
  select(cat_cmd) %>% 
  write_csv('cat_combi_CT.sh', col_names = F)
```
